Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-06-13 cmsb22.tex
Some answers

Note that even with a very restricted time-limit of two minutes, it was possible with the proposed technique to find \emph{all} minimal trap spaces of small models (roughly under 130 nodes, i.e., considered as quite big up to now).
Though it might seem impractical to handle tens of thousands of such possible complex attractors in a manual way, i.e., to compare them to specific experimental conditions and corresponding data, we hope that an automatic analysis of such attractors might become possible with systematic verification methods, not unlike that described in~\cite{hernandez2020computational}.

@@

@@

\sylvain{Question of reviewer 3:
Thanks to the performance improvement coming with Trappist, we now do know for sure that logical models may come with an overwhelming number of trap spaces, often exceeding 1000, which leaves the intriguing question how to evaluate these 1000 or more (even with Trappist so far not always computable) attractors/phenotypes?}

>>>>

Note that even with a very restricted time-limit of two minutes, it was possible with the proposed technique to find \emph{all} minimal trap spaces of small models (roughly under 130 nodes, i.e., considered as quite big up to now).
Though it might seem impractical to handle tens of thousands of such possible complex attractors in a manual way, i.e., to compare them to specific experimental conditions and corresponding data, we hope that an automatic analysis of such attractors might become possible with systematic verification methods, not unlike that described in~\cite{hernandez2020computational}.
Since the ASP code generated is also quite declarative by nature, it is also possible to add to it supplementary constraints coming from the modeller in case one is looking for specific attractors.

@@

Note that though enumerating the extremal siphons of a Petri net is exponential(see~\cite{nabli2016enumerating} for instance) this is apparently not the bottleneck of the proposed method, showing once again that networks obtained from biochemical models do have a specific structure.

@@
